Grappa: Scalable Computing on Commodity Hardware \\for Irregular Applications

### 2012-07-23 doc/asplos13/evaluation.tex
basic performance stuff

@@

\subsubsection{Unbalanced tree search in memory}

%Using 6 cores per node gave
%Grappa up to a 20\% benefit at each data point, but Grappa could not run
%well beyond 90 machines with this core configuration because of the
%current network aggregator designa.

We ran UTS-mem on Grappa and the XMT with a binomial and two geometric
100M-vertex trees (T3L,T1L,T2L), a geometric 1.6B-vertex tree (T1XL),
and a geometric 4.2B-vertex tree (T1XXL). Both systems do relatively
poorly on the binomial tree because it is very deep and a traversal
produces too little parallelism. Figure~\ref{fig:uts_compare} shows
the performance in terms of number of vertices visited per second versus
number of compute nodes. The Grappa results shown are for 6 cores per
node and the best parameter values from a search over runtime and
application parameters.

@@

\TODO{ we still win with th=1 }

\subsubsection{BFS}

@@

Figure~\ref{fig:bfs-performance} shows Grappa's performance on BFS
compared to that of the XMT.\footnote{The performance dip at 112 nodes is not an anomaly; it is highly repeatable.  Despite extensive investigation on our part, we can find no reasonable explanation for it.} There are
two things to observe. First, At 128 XMT processors/cluster nodes,
the XMT is  4.17 times faster than Grappa. This is due to the
XMT's faster network: the XMT is able to issue 100 million network
requests per second per node; at the 128 nodes datapoint, Grappa is
aggregating 25 million network requests per second, or 4 times slower.
\checkme{Second, Grappa is scaling...}

@@

Figure~\ref{fig:centrality-performance} shows Grappa's performance on
Betweenness Centrality compared to that of the XMT. At 128 XMT
processors/cluster nodes, the XMT is 1.75 times faster than Grappa.
\TODO{Add more here...}

>>>>

We evaluate Grappa in four ways. First, we evaluate its performance
with respect to the XMT. Second, we explore the benefit that
aggregation gives us. Third, we investigate sensitivity of two key
parameters in the runtime. Fourth, we investigate scaling.

@@

To evaluate Grappa's preformance with respect to the XMT, we ran each
of our three benchmarks on up to 16 nodes of each machine. Grappa used
6 cores per node, with the best parameters chosen for each point. The
XMT could not run on 2 nodes, so the point is omitted.

@@

\paragraph{Unbalanced tree search} We ran UTS-mem with a geometric 100M-vertex tree
(T1L). Figure~\ref{fig:uts_compare} shows the performance in terms of
number of vertices visited per second versus number of compute
nodes. Grappa is 3.2 times faster than the XMT at 16 nodes.

@@

\paragraph{BFS}

We ran BFS on a synthetic Kronecker graph with $2^{25}$ vertices and
$2^{29}$ edges (25 GB of data). Figure~\ref{fig:bfs-performance} shows
our performance in terms of graph edges traversed per second . The XMT
is 2.5 times faster than Grappa at 16 nodes.

@@

We ran Betweenness Centrality on the same scale 25 Kronecker graph as
we did for BFS. Figure~\ref{fig:centrality-performance} shows our
performance in terms of graph edges traversed per second. At 16 XMT
processors/cluster nodes, the XMT is 1.75 times faster than Grappa.
